Lossy compression of DNA sequencing quality data

### 2015-04-07 manuscript/q-compression.tex
Fixed column labeling issue in mapping results table (Table 2).

\begin{tabular}{lr|cc|cc|cc|cc|cc}
&  & \multicolumn{2}{c|}{{\em Profile (256)}} & \multicolumn{2}{c|}{{\em QualComp (6)}} & \multicolumn{2}{c|}{{\em QualComp (10)}} & \multicolumn{2}{c|}{{\em QualComp (30)}} & \multicolumn{2}{c}{{\em QualComp (100)}} \\
& &  kept & discarded & kept & discarded & kept & discarded & kept & discarded & kept & discarded \\ 
\cline{2-12}
& mapped & 892051 & 562 & 891375 & 1238 & 891777 & 836 & 892233 & 380 & 892454 & 159 \\ 
{\em original}  & unmapped & 119 & 132702 & 304 & 132517 & 265 & 132556 & 220 & 132601 & 172 & 132649 \\ 
\cline{2-12}
& sum & 892170 & 133264 & 891679 & 133755 & 892042 & 133392 & 892453 & 132981 & 892626 & 132808 \\

>>>>

\begin{tabular}{lr|cc|cc|cc|cc|cc}
&  & \multicolumn{2}{c|}{{\em Profile (256)}} & \multicolumn{2}{c|}{{\em QualComp (6)}} & \multicolumn{2}{c|}{{\em QualComp (10)}} & \multicolumn{2}{c|}{{\em QualComp (30)}} & \multicolumn{2}{c}{{\em QualComp (100)}} \\
& &  mapped & unmapped & mapped & unmapped & mapped & unmapped & mapped & unmapped & mapped & unmapped \\ 
\cline{2-12}
& mapped & 892051 & 562 & 891375 & 1238 & 891777 & 836 & 892233 & 380 & 892454 & 159 \\ 
{\em original}  & unmapped & 119 & 132702 & 304 & 132517 & 265 & 132556 & 220 & 132601 & 172 & 132649 \\ 
\cline{2-12}
& sum & 892170 & 133264 & 891679 & 133755 & 892042 & 133392 & 892453 & 132981 & 892626 & 132808 \\
